Interactive Summarization of Relational Tables

### 2014-11-15 TableSummarization/Paper/intro.tex
changes

However, there are cases where drill-down is ineffective; 
for example, when the number of distinct values
in a column is large, vanilla drill-down 
could easily overwhelm analysts by presenting them with too many 
results (i.e., aggregates). 
Further, drill-down only allows us to instantiate values
in one column at a time, instead of allowing simultaneous drill-downs
on multiple columns---simultaneous drill-down on multiple columns 
could once again suffer from the problem
of having too many results, stemming from distinct combinations of column values.

In this paper, we present a new interaction operator 
that is an extension to a traditional 
drill-down operator, aimed at providing {\em complementary}
functionality to drill-down in cases where drill-down is
ineffective. We call our operator {\em smart drill-down}.
At a high level, smart drill-down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill-down.
Note that our goal is to {\em not} replace traditional 
drill-down functionality, which we believe is essential;
instead, our goal is to provide auxiliary functionality 
which the analyst is free to use whenever they find 
traditional drill-downs ineffective.

>>>>

However, there are cases where drill-down is ineffective; 
for example, when the number of distinct values
in a column is large, vanilla drill-down 
could easily overwhelm analysts by presenting them with too many 
results (i.e., aggregates). 
Further, drill-down only allows us to instantiate values
in one column at a time, instead of allowing simultaneous drill-downs
on multiple columns---simultaneous drill-down on multiple columns 
could once again suffer from the problem
of having too many results, stemming from many distinct combinations of column values.

In this paper, we present a new interaction operator 
that is an extension to a traditional 
drill-down operator, aimed at providing {\em complementary}
functionality to drill-down in cases where drill-down is
ineffective. We call our operator {\em smart drill-down}.
At a high level, smart drill-down lets analysts zoom into
the more ``interesting'' parts of a table or a database,
with fewer operations, and without having to examine as much
data as traditional drill-down.
Note that our goal is {\em not} to replace traditional 
drill-down functionality, which we believe is fundamental;
instead, our goal is to provide auxiliary functionality 
which the analyst is free to use whenever they find 
traditional drill-downs ineffective.
